Additional analysis

### 2019-03-08 README.Rmd
Add dual licensing details

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code :** See the [DESCRIPTION](DESCRIPTION) file

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

>>>>

**Text and figures:** All prose and images are licensed under Creative Commons ([CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/))

**Code:** With only two exceptions, all the code is dual-licensed under the [MIT License](LICENSE.md) and [GPL 3](https://www.gnu.org/licenses/gpl-3.0.en.html). Two dependencies related to Stan compilation—[`R/stanmodels.R`](R/stanmodels.R) and [`tools/make_cc.R`](tools/make_cc.R)—are licensed as GPL 3 only, and we can't backwards-license them as only MIT. Additionally, any binary files generated by those files (i.e. the compiled Stan code) is inherently GPL-licensed, which also makes this entire project GPL-licensed in the end. But since we've dual-licensed pretty much everything else, you treat everything as MIT unless a file is explicitly GPL-only.

*(Here are a bunch of resources about the vagaries of mixing MIT and GPL licenses: [link](https://github.com/ropensci/unconf17/issues/32); [link](https://github.com/stan-dev/rstantools/issues/17); [link](https://opensource.stackexchange.com/questions/1640/if-im-using-a-gpl-3-library-in-my-project-can-i-license-my-project-under-mit-l))*
